Predicting the 2024 U.S. Presidential Election: Trump’s Likely Victory Based on Polling Analysis

### 2024-11-03 paper/paper.qmd
committing changes to paper.qmd

# Reshape the data for ggplot
state_predictions_long <- predicted_results %>%
  pivot_longer(cols = c(harris_pct, trump_pct), 
               names_to = "candidate", 
               values_to = "winning_probability") %>%
  mutate(candidate = recode(candidate, 
                            harris_pct = "Kamala Harris", 
                            trump_pct = "Donald Trump"))

# Create the bar chart
ggplot(state_predictions_long, aes(x = state, y = winning_probability, fill = candidate)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +  # Flip coordinates for horizontal bars
  scale_fill_manual(values = c("blue", "red")) +  # Specify colors
  labs(title = "Predicted Winning Percentages by Battleground State on Election Day",
       x = "Winning Probability (%)",
       y = "State") +
  theme_minimal() +
  theme(legend.title = element_blank())  # Remove legend title

>>>>

# Reshape the data for ggplot
state_predictions_long <- state_predictions %>%
  pivot_longer(cols = c(harris_pct, trump_pct), 
               names_to = "candidate", 
               values_to = "winning_probability") %>%
  mutate(candidate = recode(candidate, 
                            harris_pct = "Kamala Harris", 
                            trump_pct = "Donald Trump"))

# Create the bar chart
ggplot(state_predictions_long, aes(x = state, y = winning_probability, fill = candidate)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +  # Flip coordinates for horizontal bars
  scale_fill_manual(values = c("red", "blue")) +  # Specify colors
  labs(title = "Predicted Winning Percentages by Battleground State on Election Day",
       x = "Winning Probability (%)",
       y = "State") +
  theme_minimal() +
  theme(legend.title = element_blank())  # Remove legend title
